\section{Threats to Validity}~\label{sec:threats}

\subsection{Project Risks}

\subsubsection{Technical limitations}

\textbf{Risk}

Quantum computing technologies are new and undeveloped, with practical implementations potentially unsuitable or impossible given the current state of the technology. These limitations may hinder achieving of the research objectives.

\textbf{Mitigation}

If this limitation is affronted, either reduce scope, or trial alternative approaches.
% 
\subsubsection{Data quality}

\textbf{Risk}

The quality of the data may be insufficient: as the acquisition of real data was deemed impractical, generated data were used and as a result of limited time and scope, it may be non-representative or inadequate for achieving all research objectives. 

\textbf{Mitigation}

Improve the radar data models and validate it with additional data sources to ensure a representative dataset. 
% 
\subsubsection{Time constraints}

\textbf{Risk}

Since the honours thesis is inherently time constrained, the project timeline and deadlines may prove insufficient to thoroughly explore and answer all research questions.
Furthermore, inadequate time management could result in rushed or incomplete work-products, and thereby potentially compromise the quality of the research.

\textbf{Mitigation}

Create a detailed project plan with definite milestones and deadlines. Seek guidance from supervisor to ensure time management and focus are maintained.
% 
\subsubsection{Scope creep}

\textbf{Risk}

The research project may face the risk of scope creep, wherein additional objectives, or analysis – outside of scope - are added. This may lead to a loss of methodological rigor and risk of not achieving the defined research objectives.

\textbf{Mitigation}

Define the research scope and objectives clearly from the beginning. If a scope change is required, seek advice from supervisor and produce a written deviation justification.
% 
\subsubsection{Ethical considerations}

\textbf{Risk}

While no serious ethical concerns were raised, there is a small risk that this research could be deemed sensitive, which risks any future dissemination plans.

\textbf{Mitigation}

Review security assessments and maintain transparent documentation throughout the process.
% 
\subsubsection{Resource limitations}

\textbf{Risk}

Due to this research requiring access to cloud-hosted quantum computers, a lack of funding for this service may impact the ability to achieve the research objectives.

\textbf{Mitigation}
Seek whether physical hardware is required, and if so, optimise resource usage by prioritising critical experiments. Cost limitations could be mitigated by seeking funding from the university.
